---
title: "Endogeneity Simulation"
author: "Cort W. Rudolph"
date: "September 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Required Packages
```{r message=FALSE, warning=FALSE}
library(simstandard)
library(lavaan)
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
library(AER)
```

# lavaan syntax for populationmodel
```{r}
populationModel <- '
Y ~ .50*X
Y ~ .50*Z
X ~ .50*Z
'
```

# Simulate data
```{r}
set.seed(1818)
data <- sim_standardized(populationModel, n = 100000)
```

# Generate Instrument
*Note:* e_X is the residual variance (i.e., error) of X from our model; it is the part of X that is unexplained  by Z
```{r}
set.seed(1818)
TEMP <- rnorm(nrow(data)) # Creating some "noise"
data$Z_instrument <- data$e_X + TEMP # Adding some "noise"
```

# Correlations
```{r}
cor(data)
```

# Replicate Population Model
```{r}
sampleModel <- '
Y ~ X + Z
X ~ Z
'
sem(sampleModel, data) %>% parameterestimates()
```

# Model 1 - Endogenous Predictor
```{r}
sampleModel <- 'Y ~ X'
sem(sampleModel, data) %>% parameterestimates()
```

# Model 2 - 2SLS
```{r}
sampleModel <- '
Y ~ X
Y ~~ X
X ~ Z_instrument
'
sem(sampleModel, data) %>% parameterestimates()
```



# Check work using `ivreg` from `AER` (n.b., parameter estimates are equivalent)
- Note form of equation: y ~ endogenous|instrument
- More Here: https://rpubs.com/wsundstrom/t_ivreg
```{r message=FALSE}
ivregMod <- ivreg(Y ~ X|Z_instrument,  data = data)
summary(ivregMod, vcov = sandwich, df = Inf, diagnostics = TRUE)
```













































